Pathogen Spillover - dissertation chapter

### 2016-09-01 pathogen-spillover-diss-ch.Rmd
Add back bay laurel density variable.

```{r load data, echo=F, message=F}
library(knitr)
load("climate_path_model_data.RData")
library(piecewiseSEM)# version 1.1.1, tried most recent version & kept getting errror 7/18/2016 b/c matrices rows were unequal in sem.missing.paths function
library(dplyr, verbose = F)
library(lme4, verbose = F)
library(lmerTest, verbose = F)

@@

      wet_hours_1422 <- lmer(avg_hrs1422_wet_t_t1.log ~ umca_density_ha.log + (1|plotid) + (1|sample_year), data = oakplots.sub),

      hrs_abv25 <- lmer(hrs_abv25ds ~ twi15m.log + (1|plotid) + (1|sample_year), data = oakplots.sub),

@@

      wet_hours_1422 <- lmer(avg_hrs1422_wet_t_t1.log.scl ~ umca_density_ha.log.scl + (1|plotid) + (1|sample_year), data = oakplots.sub),

      hrs_abv25 <- lmer(hrs_abv25ds.scl ~ twi15m.log.scl + (1|plotid) + (1|sample_year), data = oakplots.sub),

>>>>

```{r load data, echo=F, message=F}
library(knitr)
load("climate_path_model_data.RData")
library(piecewiseSEM)# version 1.1.1, tried most recent version & kept getting errror 7/18/2016 b/c matrices rows were unequal in sem.missing.paths function
library(plyr); library(dplyr, verbose = F)
library(lme4, verbose = F)
library(lmerTest, verbose = F)

@@

      wet_hours_1422 <- lmer(avg_hrs1422_wet_t_t1.log ~ umca_density_ha.log + twi15m.log + (1|plotid) + (1|sample_year), data = oakplots.sub),

      hrs_abv25 <- lmer(hrs_abv25ds ~ umca_density_ha.log + twi15m.log + (1|plotid) + (1|sample_year), data = oakplots.sub),

@@

      wet_hours_1422 <- lmer(avg_hrs1422_wet_t_t1.log.scl ~ umca_density_ha.log.scl + twi15m.log.scl + (1|plotid) + (1|sample_year), data = oakplots.sub),

      hrs_abv25 <- lmer(hrs_abv25ds.scl ~ umca_density_ha.log.scl + twi15m.log.scl + (1|plotid) + (1|sample_year), data = oakplots.sub),
